Weather Data Integration and Assimilation System\\

### 2020-02-10 results/sec_1-test_plan.tex
..

\subsection{Performance Metrics of Load Testing}
\label{subse:test_plan_metrics}
During the performance analysis, following metrics are use to measure the performance of the system.
\begin{itemize}
    \item Throughput - Number of requests that can be process per unit time. Normally for \acrshort{wdias} performance observations, it uses \acrfull{rps} in order to measure the throughput.
    \item Latency - Time taken for response back to the sent request to the system. Normally it measures with milliseconds (ms) in the \acrshort{wdias}. During the performance analysis, it measures the minimum response time, maximum response time, the average response time, and standard deviation. The standard deviation measures the mean distance of the values to their average.It gives an idea of the dispersion or variability of the measures to their mean value. So, if the deviation value is low compared to the mean value, it will indicate that the measures are not dispersed (or mostly close to the mean value) and that the mean value is significant. Other than that, it measure the response time into 90\% percentile, while gives best response time up to 90\% percent of the responses.
    \item Resource Utilization - Resource Utilization is calculated based on the CPU and Memory usage via \acrshort{k8s} metrics server. It calculates the resource utilization over 60 seconds of time window. Network usage is getting based on the actual physical machines.
    \item Auto Scaling - The \acrshort{wdias} is running with two configurations. First is, since it is running the microservice as docker containers, it allow to increase or shrink the resource usage and share the resources within a physical machine. Second is, running with auto scaling enabled for the microservice which are using higher resources.
\end{itemize}

>>>>

\subsection{Performance Metrics of Load Testing}
\label{subse:test_plan_metrics}
During the performance analysis, following metrics are use to measure the performance of the system.
\begin{itemize}
    \item \emph{Throughput} - Number of requests that can be process per unit time. Normally for \acrshort{wdias} performance observations, it uses \acrfull{rps} in order to measure the throughput.
    \item \emph{Latency} - Time taken for response back to the sent request to the system. Normally it measures with milliseconds (ms) in the \acrshort{wdias}. During the performance analysis, it measures the minimum response time, maximum response time, the average response time, and standard deviation. The standard deviation measures the mean distance of the values to their average.It gives an idea of the dispersion or variability of the measures to their mean value. So, if the deviation value is low compared to the mean value, it will indicate that the measures are not dispersed (or mostly close to the mean value) and that the mean value is significant. Other than that, it measure the response time into 90\% percentile, while gives best response time up to 90\% percent of the responses.
    \item \emph{Resource Utilization} - Resource Utilization is calculated based on the CPU and Memory usage via \acrshort{k8s} metrics server. It calculates the resource utilization over 60 seconds of time window. Network usage is getting based on the actual physical machines.
    \item \emph{Auto Scaling} - The \acrshort{wdias} is running with two configurations. First is, since it is running the microservice as docker containers, it allow to increase or shrink the resource usage and share the resources within a physical machine. Second is, running with auto scaling enabled for the microservice which are using higher resources.
\end{itemize}
